\section{Peer-Reviewed Publications}
\begin{itemize}
\item Google Scholar total number of citations: 1244
\item h-index: 14
\item i10-index: 16
\end{itemize}

\begin{enumerate}
  \item Lindsay, Alexander, Guillaume Giudicelli, Peter German, John Peterson, Yaqi Wang, Ramiro Freile, David Andrs et al. "MOOSE Navier–Stokes module." SoftwareX 23 (2023): 101503.
  \item DeChant, Corey, Casey Icenhour, Shane Keniley, Grayson Gall, Alexander Lindsay, Davide Curreli, and Steven Shannon. "Verification and validation of the open-source plasma fluid code: Zapdos." Computer Physics Communications 291 (2023): 108837.
  \item Recuero, Antonio, Alexander Lindsay, and Dewen Yushu. "An approach to grid-to-rod fretting wear modeling using dynamic mortar contact." Progress in Nuclear Energy 163 (2023): 104793.
  \item Recuero, Antonio, and Alexander Lindsay. "On practical aspects of variational consistency in contact dynamics." Journal of Computational and Nonlinear Dynamics 18, no. 8 (2023): 081003.
  \item DeChant, Corey, Casey Icenhour, Shane Keniley, Alexander Lindsay, Grayson Gall, Kimberly Clein Hizon, Davide Curreli, and Steven Shannon. "Verification methods for drift–diffusion reaction models for plasma simulations." Plasma Sources Science and Technology 32, no. 4 (2023): 044006.
  \item Lindsay, Alexander D., Derek R. Gaston, Cody J. Permann, Jason M. Miller, David Andrš, Andrew E. Slaughter, Fande Kong et al. "2.0-MOOSE: Enabling massively parallel multiphysics simulation." SoftwareX 20 (2022): 101202.
  \item Dhulipala, Somayajulu LN, Chandrakanth Bolisetti, Lynn B. Munday, William M. Hoffman, Ching‐Ching Yu, Faizan Ul Haq Mir, Fande Kong, Alexander D. Lindsay, and Andrew S. Whittaker. "Development, verification, and validation of comprehensive acoustic fluid‐structure interaction capabilities in an open‐source computational platform." Earthquake Engineering \& Structural Dynamics (2022).
  \item Recuero, Antonio, Alexander Lindsay, Dewen Yushu, John W. Peterson, and Benjamin Spencer. "A mortar thermomechanical contact computational framework for nuclear fuel performance simulation." Nuclear Engineering and Design (2022): 111808.
  \item Weiss, Abdullah G., Laith J. Zaidan, Mohammad TH Bani Ahmad, M. Gomaa Abdoelatef, John W. Peterson, Alexander D. Lindsay, Fande Kong, Karim Ahmed, and Mark L. Kimber. "Characterization of the Finite Element Computational Fluid Dynamics Capabilities in the Multiphysics Object Oriented Simulation Environment." Journal of Nuclear Engineering and Radiation Science 9, no. 2 (2022): 021402.
  \item Abou-Jaoude, A., Harper, S., Giudicelli, G., Balestra, P., Schunert, S., Martin, N., Lindsay, A., Tano, M. and Freile, R., 2021. A workflow leveraging MOOSE transient multiphysics simulations to evaluate the impact of thermophysical property uncertainties on molten-salt reactors. Annals of Nuclear Energy, 163, p.108546.
  \item Lindsay, A., Stogner, R., Gaston, D., Schwen, D., Matthews, C., Jiang, W., Aagesen, L.K., Carlsen, R., Kong, F., Slaughter, A. and Permann, C., 2021. Automatic Differentiation in MetaPhysicL and Its Applications in MOOSE. Nuclear Technology, pp.1-18.
  \item Martineau, R., Andrs, D., Carlsen, R., Gaston, D., Hansel, J., Kong, F., Lindsay, A., Permann, C., Slaughter, A., Merzari, E. and Hu, R., 2020. Multiphysics for nuclear energy applications using a cohesive computational framework. Nuclear Engineering and Design, 367, p.110751.
  \item Permann, Cody J., Derek R. Gaston, David Andrš, Robert W. Carlsen, Fande Kong, Alexander D. Lindsay, Jason M. Miller et al. "MOOSE: Enabling massively parallel multiphysics simulation." SoftwareX 11 (2020): 100430.
  \item Kong, F., Wang, Y., Gaston, D.R., Permann, C.J., Slaughter, A.E., Lindsay, A.D., DeHart, M.D. and Martineau, R.C., 2020. A Highly Parallel Multilevel Newton--Krylov--Schwarz Method with Subspace-Based Coarsening and Partition-Based Balancing for the Multigroup Neutron Transport Equation on Three-Dimensional Unstructured Meshes. SIAM Journal on Scientific Computing, 42(5), pp.C193-C220.
  \item Peterson, J., Lindsay, A., \& Kong, F. Overview of the Incompressible Navier-Stokes simulation capabilities in the MOOSE Framework. \textit{Advances in Engineering Software}, 119, 68-92
  \item Lindsay, A., Ridley, G., Rykhlevskii, A., \& Huff, K. Introduction to Moltres: An application for simulation of Molten Salt Reactors. \textit{Annals of Nuclear Energy}, 114, 530-540
  \item Lindsay, A., Graves, D., \& Shannon, S. Fully Coupled Simulation
  of the Plasma Liquid Interface and Interfacial Coefficient
  Effects. \textit{Journal of Physics D: Applied Physics}, 49(23), 235204
  \item Anderson, C., Cha, N., Lindsay, A., Clark, D., \& Graves, D. The
  Role of Interfacial Reactions in Determining Plasma-Liquid
  Chemistry. \textit{Plasma Chemistry and Plasma Processing}, 36(6), 1393-1415
  \item Lindsay, A., Anderson, C., Shannon, S., \& Graves, D. (2015) Momentum, Heat, and Neutral Mass Transport in Convective Atmospheric Pressure Plasma-Liquid Systems and Implications for Aqueous Targets. \textit{Journal of Physics D: Applied Physics}, 48, 424007
  \item Lindsay, A., Byrns, B., King, W., Andhvarapou, A., Fields, J., Knappe, D., Fonteno, W., \& Shannon, S. (2014). Fertilization of Radishes, Tomatoes, and Marigolds Using a Large-Volume Atmospheric Glow Discharge. \textit{Plasma Chemistry and Plasma Processing}, 34(6), 1271-1290.
  \item Byrns, B., Wooten, D., Lindsay, A., \& Shannon, S. (2012). A VHF driven coaxial atmospheric air plasma: electrical and optical characterization. \textit{Journal of Physics D: Applied Physics}, 45(19), 195204.
  \item Manner, V. W., Lindsay, A. D., Mader, E. A., Harvey, J. N., \& Mayer, J. M. (2012). Spin-forbidden hydrogen atom transfer reactions in a cobalt biimidazoline system. \textit{Chemical Science}, 3(1), 230-243.
  \item Liang, W., Isborn, C. M., Lindsay, A., Li, X., Smith, S. M., \& Levis,
    R. J. (2010). Time-Dependent Density Functional Theory Calculations of
    Ehrenfest Dynamics of Laser Controlled Dissociation of NO+: Pulse Length and
    Sequential Multiple Single-Photon Processes. \textit{The Journal of Physical
      Chemistry A}, 114(21), 6201-6206.
\end{enumerate}
